Limb-darkening and exoplanets II: Choosing the Best Law for Optimal Retrieval of Transit Parameters

### 2016-01-21 second_submission/which_law_2_use.tex
Corrected typo.

From the results on the past sub-section, one can see that for a given set of stellar and transit parameters, a law can be chosen in order to minimize the 
biases in the retrieved transit parameters from the transit light curve. However, an interesting question is whether the precision of a given lightcurve can 
actually provide enough precision in order to use a more complex parametrization of the limb-darkening effect and, depending on the answer, what is 
the cost. Fitting a complex law to a noisy light curve will definitely lower the precision of the retrieved transit parameters due to the high flexibility of the 
model, while fitting a law that is too simple for a very precise lightcurve will most definitely lead to larger 
biases, due to the strictness of the chosen model. This problem is known as the bias-variance trade-off. Probabilistically, for a given estimator $\hat{\theta}$ of the parameter $\theta$, we will be interested in its variance (whose 
square-root defines the inverse precision), $\textnormal{Var}[\hat{\theta}]$, and its bias, defined as $\mathbb{E}[\hat{\theta}]-\theta$, where 
$\mathbb{E}[\cdot]$ defines the expectation value and $\textnormal{Var}[\cdot]$ is the variance operator. The bias, on one hand, defines how far on average is 
the estimator from the parameters' true value, while the variance defines the spread around the expected value of the estimator (see Figure \ref{bias-variance-plot}). 
One ideally wants a low-bias and high-precision estimator, which is both close to the real value of the parameter on average and, 
at the same time, has a low spread around such value. The problem is that in real applications one has the possibility to choose from various estimators with different 
ammounts of bias and variance, and thus choosing among them is, at first, not trivial. This is when the mean-squared error metric comes in handy. The mean-squared 
error (MSE) of an estimator $\hat{\theta}$ of the parameter $\theta$ is defined as
\begin{eqnarray*}
\textnormal{MSE} &=& \mathbb{E}[(\theta - \hat{\theta})^2].
\end{eqnarray*}
From the definition of the MSE, it can be seen that it is a measure of the square of the distance from the estimator to the parameters' ``true" value. This provides a metric among a given suite of estimators for a given parameter: the one that gives the minimum mean-squared error 
provides, on average, the one that is closer to the underlying ``true" value on a mean-square sense. Furthermore, it is easy to show that the MSE can be written 
as
\begin{eqnarray*}
\textnormal{MSE} &=& \mathbb{E}[(\theta - \hat{\theta})^2], \\
&=& (\mathbb{E}[\hat{\theta}]-\theta)^2 + \textnormal{Var}[\hat{\theta}],\\
&=& \textnormal{Bias}^2 + \textnormal{Variance}.
\end{eqnarray*}
This implies that given the bias and the variance of an estimator, the MSE can be easily calculated. In our specific application, in the past sub-section we have already 
shown and studied the biases that each limb-darkening law (i.e., different estimators) imply on the retrieved transit parameters through simulation. We have thus already
calculated the floor of the MSE for each law, and it only remains to study the variances implied by those limb-darkening laws, which is a function of the noise of the lightcurve 
used to retrieve the transit parameters.

>>>>

From the results on the past sub-section, one can see that for a given set of stellar and transit parameters, a law can be chosen in order to minimize the 
biases in the retrieved transit parameters from the transit light curve. However, an interesting question is whether the precision of a given lightcurve can 
actually provide enough precision in order to use a more complex parametrization of the limb-darkening effect and, depending on the answer, what is 
the cost. Fitting a complex law to a noisy light curve will definitely lower the precision of the retrieved transit parameters due to the high flexibility of the 
model, while fitting a law that is too simple for a very precise lightcurve will most definitely lead to larger 
biases, due to the strictness of the chosen model. This problem is known as the bias-variance trade-off. Probabilistically, for a given estimator $\hat{\theta}$ of 
the parameter $\theta$, we will be interested in its variance (whose inverse defines the precision), $\textnormal{Var}[\hat{\theta}]$, and its bias, defined as 
$\mathbb{E}[\hat{\theta}]-\theta$, where $\mathbb{E}[\cdot]$ defines the expectation value and $\textnormal{Var}[\cdot]$ is the variance operator. The bias, on 
one hand, defines how far on average is the estimator from the parameters' true value, while the variance defines the spread around the expected value of the 
estimator (see Figure \ref{bias-variance-plot}). One ideally wants a low-bias and high-precision estimator, which is both close to the real value of the parameter on average and, 
at the same time, has a low spread around such value. The problem is that in real applications one has the possibility to choose from various estimators with different 
ammounts of bias and variance, and thus choosing among them is, at first, not trivial. This is when the mean-squared error metric comes in handy. The mean-squared 
error (MSE) of an estimator $\hat{\theta}$ of the parameter $\theta$ is defined as
\begin{eqnarray*}
\textnormal{MSE} &=& \mathbb{E}[(\theta - \hat{\theta})^2].
\end{eqnarray*}
From the definition of the MSE, it can be seen that it is a measure of the square of the distance from the estimator to the parameters' ``true" value. This provides a metric among a given suite of estimators for a given parameter: the one that gives the minimum mean-squared error 
provides, on average, the one that is closer to the underlying ``true" value on a mean-square sense. Furthermore, it is easy to show that the MSE can be written 
as
\begin{eqnarray*}
\textnormal{MSE} &=& \mathbb{E}[(\theta - \hat{\theta})^2], \\
&=& (\mathbb{E}[\hat{\theta}]-\theta)^2 + \textnormal{Var}[\hat{\theta}],\\
&=& \textnormal{Bias}^2 + \textnormal{Variance}.
\end{eqnarray*}
This implies that given the bias and the variance of an estimator, the MSE can be easily calculated. In our specific application, in the past sub-section we have already 
shown and studied the biases that each limb-darkening law (i.e., different estimators) imply on the retrieved transit parameters through simulation. We have thus already
calculated the floor of the MSE for each law, and it only remains to study the variances implied by those limb-darkening laws, which is a function of the noise of the lightcurve 
used to retrieve the transit parameters.
